### 2019-07-05 README.Rmd
commit

## Example

This is a basic example which shows you how to use this package:

```{r example}
library(ggmatplot)

iris_sub <- subset(iris, Species == "setosa")

@@

>>>>

Below are some basic examples which show you how to use this package.

### Example 1

```{r load_package, echo=FALSE, message=FALSE, warning=FALSE}
library(ggmatplot)
```

```{r example1}
X <- 1:10
Y=X^2
Z=X^2-2*X

# Original way by matplot function
matplot(X,cbind(Y,Z),pch=c(16,1),xlab="x",ylab="X^2 and X^2-2*X")
legend(1,100,legend=c("y","Z"),pch=c(16,1))

# Use ggmatplot
ggmatplot(X,cbind(Y,Z), shape = c(16,1),legend_label =  c("X^2","X^2-2*X"),legend_title = "")
```

#### Example 2: Iris data

```{r example2}
iris_sub <- subset(iris, Species == "setosa")

@@

### Example 3: Linear regression

```{r example3}
x <- rnorm(100,sd=2)
y <- x*0.5+rnorm(100,sd=1)
fit.y <- fitted(lm(y~x))
ggmatplot(x,cbind(y,fit.y))
```
